### 2018-07-03 pack/prv/opt/tokipona/aux/article/acm/samplebody-journals.tex
feito roteiro basico de uso do pacote em python

\subsection{Statistics of the vocabulary}\label{sec:stat}
This section focuses on the statistics of the vocabulary
and of the syntactic rules:
the letters, phonemes, word sizes,
possible combinations for words and sentences.
% The statistics are in Appendix~\cite{listings},
% and the next paragraph is an overview. TTM
The script \tttt{makeStatistics.py}
was used to obtain all the measurements and tables
discussed herein,
and hold further measurements and sets of words
regarded as less suitable for this exposition than
for a deeper investigation.

>>>>

\subsection{Statistics of the vocabulary}\label{sec:stat}
This section focuses on the statistics of the vocabulary
and of the syntactic rules:
the letters, phonemes, word sizes,
possible combinations for words and sentences.
% The statistics are in Appendix~\cite{listings},
% and the next paragraph is an overview. TTM
The class \tttt{TPTabFig}
was used to obtain all the measurements and tables
discussed herein,
and hold further measurements and sets of words
regarded as less suitable for this exposition than
for a deeper investigation.\cite{prv}
